
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
	{#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
	\item\small{
    	{#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
	\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
  	\textbf{#1} & \textbf{\small #2} \\
  	\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
  	\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
	\item
	\begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
  	\small#1 & \textbf{\small #4}\\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
	{\Huge \scshape ABDUL DANISH} \\ \vspace{1pt}
	Hyderabad, India. \\ \vspace{1pt}
	\small \raisebox{-0.1\height}\faPhone\ +91 6300339358 ~ \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{abduldanish109@gmail.com}} ~
	\href{https://linkedin.com/in//}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/abdul-danish-120872225}}
	\vspace{-8pt}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
	\resumeSubheading
  	{DigitalDots Technologies Pvt Ltd}{Nov 2022 -- Present}
  	{Java Backend Developer}{Hyderabad, India}
  	\resumeItemListStart
    	\resumeItem{Played a key role in Building the Low code platform (Evolve) aimed at accelerating the Digital Transformation
         journey for enterprises by infusing AI to power the composite business orchestrations and enable business models on the cloud. }
        \resumeItem{Active participation in product design thinking sessions to analyze functional specifications and help definition of product user experience and define \textbf{API Swagger} specifications.}
        \resumeItem{Responsible for Building and maintaining Backend Services, Developing \textbf{Microservices} using \textbf{RESTFul Web Services} utilizing \textbf {Java, Spring Boot}, and relational and/or NoSQL databases \textbf{PostgreSQL/MongoDB} while implementing various \textbf{Design patterns} to improve scalability, maintainability and performance}
        \resumeItem{Built a reusable framework using \textbf{Kafka} for the microservices to communicate with each other asynchronously.}
        \resumeItem{Hands-on experience in working with \textbf{Minio} for managing object storage and integrating file handling capabilities within the platform.}
        \resumeItem{Improved the performance of all microservices using \textbf{Redis Caching} techniques.}
        \resumeItem{Executed unit tests for various service layers and components of the application using \textbf{JUnit} and \textbf{Mockito} to ensure the correctness of the codebase by maintaining \textbf{95\%} code coverage.}
        \resumeItem{Developed and integrated custom Authorization Filters using \textbf{Spring Security} to enforce role-based access control (RBAC)
and secure Platform APIs.}
        \resumeItem{Mentored a team of 2 Junior developers with development skills and keep up with the fast-paced environment of a startup.}
	\resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------PROJECTS-----------
\section{Projects}
	\vspace{-5pt}
	\resumeSubHeadingListStart
	\resumeProjectHeading
      	{\textbf{ Workflow Automation Platform for Orchestrations} $|$ \emph
        {Java, Spring Boot, PostgreSQL, MongoDB} }{}
      	\resumeItemListStart
        	\resumeItem{Users can create, modify, and monitor multi-step workflows that integrate with external services such as APIs, databases, and message queues.}
        	\resumeItem{Built a robust, fault-tolerant orchestration engine that executes workflows with high reliability, ensuring tasks are processed in the correct sequence and with efficient error handling.}
            \resumeItem{Enabled workflows to trigger based on external events (e.g., API calls, time-based events) and perform a wide variety of automated actions such as sending emails, processing data, or invoking APIs.}
            \resumeItem{Integrated robust authentication mechanisms (OAuth, JWT) and ensured secure access to sensitive workflows, data storage, and machine learning models, following best practices for user privacy and data protection.}
            \resumeItem{Implemented Spring Batch based cloning solutions to automate the end-to-end duplication of complete solutions within the platform.}
            \resumeItem{ Integrated OpenL Decisions to manage business rules and decision tables within workflows, allowing users to automate complex decision-making processes based on real-time data.}
      	\resumeItemListEnd
	   \vspace{5pt}
	\resumeSubHeadingListEnd
\vspace{-15pt}

%
%-----------Achievements-----------
% \section{Achievements [Add all kind of achievements that shows your skills]}
%  \begin{itemize}[leftmargin=0.15in, label={}]
% 	\resumeItemListStart
%     	\resumeItem{Highest rating of \textbf{ xxxx} at Codeforces, which is the top site in terms of participation of programmers across globe.}
%     	\resumeItem{Ranked under \textbf{xyz} at Codechef which ranks among the top sites for competitive programmers. Highest rating of 2299 and rated \textbf{6*}. }
%     	\resumeItem{Qualified the prestigious ACM-ICPC regionals \textbf{thrice} and ranked Z in one of the attempts. }
%     	\resumeItem{Secured all India rank of \textbf{r, s, t} respectively in Codechef's Long Challenge in the month of February, April and May xyzh among 12k+ participants.}
%     	\resumeItem{Secured all India rank of \textbf{uh} in TCS codevita 2019.}
%     	\resumeItem{Written over \textbf{0987643} articles at Geeksforgeeks, most of them being on Data Structure and Algorithms}
%     	\resumeItem{Solved more than 2000+ problems across platforms.}
%     	\resumeItem{Awarded with Geek of the year accolade from GeeksforGeeks for contribution to the community. \href{https://www.geeksforgeeks.org/geek-of-the-year/}{(Link)} }
%   	\resumeItemListEnd
%  \end{itemize}
%  \vspace{-10pt}
 
 %
%-----------Profile Links-----------
\section{Profile Links}
 \begin{itemize}[leftmargin=0.01in, label={}]
    \resumeItemListStart
    \vspace{0pt}
        \resumeItem 
            {\href{https://leetcode.com/u/Abdul_Danish/}{Leetcode}}
        
    \resumeItemListEnd
 \end{itemize}
 \vspace{-12pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
 	\textbf{Languages}{: Java, SQL} \\
        \vspace{2pt}
 	\textbf{Technologies/Frameworks}{: Spring Boot, Spring Security, Spring Data JPA, Spring Batch, Kafka, Redis} \\
         \vspace{2pt}
        \textbf{Database}{: MongoDB, PostgreSQL} \\
        \vspace{2pt}
        \textbf{Version Control}{: GIT, Github} \\
        \vspace{2pt}
        \textbf{Testing tools}{: Postman} }} \\
        \vspace{2pt}
        \textbf{Devops}{: Docker, Kubernetes, SonarLint}
 \end{itemize}
 \vspace{-10pt}

 

%-----------EDUCATION-----------
\section{Education}
\vspace{4pt}
  \resumeSubHeadingListStart
	\resumeSubheading
  	{Global Institute Of Engineering and Technology }{2018 - 2022}
  	{Bachelor of Technology in Information Technology (CGPA of 7.03)}{ Hyderabad, Telangana, India}
    \resumeSubheading
  	{Narayana Junior College }{2016 - 2018}
  	{Maths Physics and Chemistry (Percentage of 88.3)}{ Hyderabad, Telangana, India}
    \resumeSubheading
  	{Rich Monds High School }{2015 - 2016}
  	{SSC[X] (CGPA of 7.8)}{ Hyderabad, Telangana, India}
  \resumeSubHeadingListEnd



\end{document}
